---
output: github_document
---

# psql

<!-- badges: start -->
[![R-CMD-check](https://github.com/poissonconsulting/psql/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/psql/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/poissonconsulting/psql/branch/main/graph/badge.svg?token=7F2LIBp2Tt)](https://codecov.io/gh/poissonconsulting/psql)
<!-- badges: end -->

`psql` is a wrapper on `DBI` and PostgreSQL commands thus eliminating the need for users to have to learn PostgreSQL. Now R can be used for most tasks except creating the tables and schema. 

`psql` is an R package that

- open and closes the database connection within the function, no closing required

## Installation

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("poissonconsulting/psql")
```

## Set Up

### Install postgres locally by running the following 

```
brew install postgresql
```

### config file

Your database connection details should be stored in a config.yml file. 
Set the `psql.config_path` option as the file path to the config file. 
Set the `psql.value` option as the value in the config file.

Example of a config.yml file:

```
default:
  user: "postgres"
  host: 127.0.0.1
  dbname: "postgres"
  port: 5432
  password: !expr Sys.getenv("DM_PASSWORD")
```

### pgpass file

A `.pgpass` file is required (if your database has a password) when using the `psql_backup()` function. 
The [postgresql website](https://www.postgresql.org/docs/current/libpq-pgpass.html) provides details on how to set it up.

Currently add the following file named `.pgpass` to `~`
```
*:*:*:*:<password>
```
and then in the terminal run `chmod 0600 ~/.pgpass`

## Usage

Start by setting the file path for your config file in options so you do not have to pass the config file each time. 

```{r, collapse=TRUE}
library(psql)
options(psql.config_path = system.file("testhelpers/config.yml", package = "psql"))
```

Lets create a schema and table with `psql_execute_db()`

```{r, collapse=TRUE}
psql_execute_db("CREATE SCHEMA truck")
psql_execute_db(
  "CREATE TABLE truck.model (
     name TEXT NOT NULL,
     code INTEGER)"
)
```

```{r, include=FALSE}
withr::defer({
  psql_execute_db("DROP TABLE truck.model")
  psql_execute_db("DROP SCHEMA truck")
})
```

When you need to add data to a table use `psql_add_data()`, and the number of rows added will be output. 

```{r, collapse=TRUE}
model <- data.frame(
  name = c("Ranger", "F-150", "F-250"),
  code = c(2457, 1475, 1247)
)

psql_add_data(model, schema = "truck")
```

To list all the tables in the schema use `psql_list_tables()`.

```{r, collapse=TRUE}
psql_list_tables(schema = "truck")
```

To read a table in from your database use `psql_read_table()`

```{r, collapse=TRUE}
truck_models <- psql_read_table(tbl_name = "model", schema = "truck")
truck_models
```

To copy and save your database use `psql_backup()` 

```{r, eval=FALSE}
psql_backup("~/Database_backups/db_trucks_2020-07-19.sql")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/psql/issues).

[Pull requests](https://github.com/poissonconsulting/psql/pulls) are always welcome.

## Code of Conduct

Please note that the psql project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## Inspiration

- [readwritesql](https://github.com/poissonconsulting/readwritesqlite)

## Testing

In your local server you need to have a database called mydb for the tests to work. 

You also need the hosted test database credentials in your .Renviron file.
