---
output: github_document
---

# psql

<!-- badges: start -->
<!-- badges: end -->

psql is a wrapper on pg and PostgreSQL commands thus eliminating the need for users to have to learn postgres as they can use R for all required tasks except creating the tables as the datatypes and checks require manual writing. 

## Installation

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("poissonconsulting/psql")
```

## Set Up

Your database connection details should be stored in a config.yml file. 
Set the `psql.config_path` option as the file path to the config file. 
Set the `psql.value` option as the value in the config file.

Example of a config.yml file:

```
default:
  user: "postgres"
  host: 127.0.0.1
  dbname: "postgres"
  port: 5432
  password: !expr Sys.getenv("DM_PASSWORD")
```

This is needed when using the `psql_backup()` function. 
Set up a .pgpass file to also contain the password for the database.
 

## Example

This is a basic example which shows you how to solve a common problem:

``` {r, eval=FALSE}
library(psql)
## basic example code
```





## Contribution

Please report any [issues](https://github.com/poissonconsulting/psql/issues).

[Pull requests](https://github.com/poissonconsulting/psql/pulls) are always welcome.

## Code of Conduct

Please note that the psql project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
